Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-01 paper.qmd
Start working on adding langevitour

## First projection
model_prj1 <- cbind(
  c(0.37847,-0.06517,0.04231,0.01655),
  c(-0.06466,-0.27052,0.22131,-0.15235))

>>>>

```{r}
#| eval: false
langevitour::langevitour(df_model_data_two_curvy[1:(length(df_model_data_two_curvy)-1)],
                         lineFrom = distance_df_small_edges_two_curvy$from,
                         lineTo = distance_df_small_edges_two_curvy$to,
                         group = factor(df_model_data_two_curvy$type,
                                        c("data", "true mdeol","model")),
                         levelColors = c(clr_choice, '#000000', "#000000"))
```

```{r}
## First projection
model_prj1 <- cbind(
  c(0.37847,-0.06517,0.04231,0.01655),
  c(-0.06466,-0.27052,0.22131,-0.15235))
